Summary Tables

### 2020-02-12 summary_tables_outcomes.Rmd
Add whw for all scenarios

for(city in cities){
  if (!city %in% c('buenos_aires', 'mexico_city')){
    print(kable(format(round(io[[city]]$outcomes$whw$Baseline$whw)), caption = paste('Who Hit Whom (WHW) baseline matrix for ', city)))
    cat("\n")
  }
}

@@

>>>>

@@

## Who Hit Whom matrix

Who hit whom matrix for baseline for each case study

### Who hit whom matrix for baseline {#whw_baseline}

for(city in cities){
  if (!city %in% c('buenos_aires', 'mexico_city')){
    for (cs in names(io$accra$outcomes$whw)){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$whw)), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")
    }

  }
}
